Truthfulness Verification System

### 2011-02-23 trunk/proposal/paper.tex
added reference

\section{Current System}
Current system for truthfulness verification is called T-verifier, which uses two phase methods for truthfulness verification of statements. Each of these two phases rely heavily on search results returned by popular search engines. T-verifier takes the doubtful statements (DS) as input from the user along with the doubtful unit (DU). Phrase after removing DU from DS is called topic unit (TU).

@@

%\bibliography{mybib}
\bibliographystyle{alpha}

>>>>

\section{Current System}
Current system for truthfulness verification is called T-verifier \cite{tverifier}, which uses two phase methods for truthfulness verification of statements. Each of these two phases rely heavily on search results returned by popular search engines. T-verifier takes the doubtful statements (DS) as input from the user along with the doubtful unit (DU). Phrase after removing DU from DS is called topic unit (TU).

@@

\bibliographystyle{plain}
\bibliography{ref}
